### 2013-07-04 miscellaneous/sorgenfrey/sorgenfrey.tex
Refactored file system

For every $\mc{C}\subseteq\mc{B}$ which is also a base for $P$, there exists a pairwise disjoint subcover $\mc{C}'\subseteq\mc{C}$ (and thus a locally finite subcover).
\end{theorem}
\newpage
\begin{proof}
It suffices to show for $[0,1)\cap P$. We begin by constructing a collection of functions $S\subseteq \omega^{\omega_1}$ and numbers $c_s$, $d_s$ defined by those functions as follows:
  \begin{itemize}
    \item Let $S_0 = \{\emptyset\}$. Let $d_{\emptyset}=0$ and $c_{\<-1\>}=1$.
    \item Suppose $S_\alpha$ has been defined, as well as $d_s\leq c_{s\concat\<-1\>}$. For $s\in S$, consider the following:
      \begin{itemize}
        \item If $d_s = c_{s\concat\<-1\>}$, do nothing.
        \item If $d_s < c_{s\concat\<-1\>}$ and $d_s\in P$, let $S_{\alpha+1}$ contain $s\concat\<0\>$ and define $c_{s\concat\<0\>}$, $d_{s\concat\<0\>}$, $c_{s\concat\<0,-1\>}$ such that 
          \[
            d_s = c_{s\concat\<0\>} < d_{s\concat\<0\>} \leq c_{s\concat\<0,-1\>} = c_{s\concat\<-1\>}
          \]
        where $[c_{s\concat\<0\>}, d_{s\concat\<0\>})\in \mc{C}$.
        \item If $d_s < c_{s\concat\<-1\>}$ and $d_s\in P$, let $S_{\alpha+1}$ contain $s\concat\<n\>$ for all $n<\omega$ and define $c_{s\concat\<n\>}$, $d_{s\concat\<n\>}$, $c_{s\concat\<n,-1\>}$ for all $n<\omega$ such that
          \[
            d_s < \dots \leq c_{s\concat\<2,-1\>} = c_{s\concat\<1\>} < d_{s\concat\<1\>} \leq c_{s\concat\<1,-1\>} = c_{s\concat\<0\>} < d_{s\concat\<0\>} \leq c_{s\concat\<0,-1\>} = c_{s\concat\<-1\>}
          \]
        where $[c_{s\concat\<n\>}, d_{s\concat\<n\>})\in \mc{C}$ for all $n<\omega$ and $c_{s\concat\<n\>} \rightarrow d_s$.
      \end{itemize}
    \item Suppose $\alpha$ is a limit ordinal and $S_\beta$ has been defined for all $\beta<\alpha$. If $s\in\omega^\alpha$ and $t\in \bigcup_{\beta<\alpha}S_\beta$ for all $t<s$, let $S_\alpha$ contain $s$ and define $d_s = \lim_{t<s}d_t$ and $c_{s\concat\<-1\>} = \lim_{t<s} c_{t\concat\<-1\>}$.
  \end{itemize}

@@

  Finally, we notice that by defining $f\in\omega^\omega_1$ such that $f(\alpha)=n_\alpha$, then $d_{f(\alpha)}$ is an increasing sequence defined for all $\alpha<\omega_1$, which is a contradiction.
\end{proof}

>>>>

For every $\mc{C}\subseteq\mc{B}$ which is also a base for $P$, there exists a pairwise disjoint subcover $\mc{C}'\subseteq\mc{C}$ (and thus a locally finite subcover).
\end{theorem}
\newpage
\begin{proof}
It suffices to show for $[0,1)\cap P$. We begin by constructing a collection of functions $S\subseteq \omega^{\omega_1}$ and numbers $c_s$, $d_s$, $c_{s\concat\<-1\>}$ defined by those functions as follows:
  \begin{itemize}
    \item Let $S_0 = \{\emptyset\}$. Let $d_{\emptyset}=0$ and $c_{\<-1\>}=1$.
    \item Suppose $S_\alpha$ has been defined, as well as $d_s\leq c_{s\concat\<-1\>}$ for each $s\in S_\alpha$. For $s\in S_\alpha$, consider the following:
      \begin{itemize}
        \item If $d_s = c_{s\concat\<-1\>}$, do nothing.
        \item If $d_s < c_{s\concat\<-1\>}$ and $d_s\in P$, let $S_{\alpha+1}$ contain $s\concat\<0\>$ and define $c_{s\concat\<0\>}$, $d_{s\concat\<0\>}$, $c_{s\concat\<0,-1\>}$ such that 
          \[
            d_s = c_{s\concat\<0\>} < d_{s\concat\<0\>} \leq c_{s\concat\<0,-1\>} = c_{s\concat\<-1\>}
          \]
        where $[c_{s\concat\<0\>}, d_{s\concat\<0\>})\in \mc{C}$.
        \item If $d_s < c_{s\concat\<-1\>}$ and $d_s\not\in P$, let $S_{\alpha+1}$ contain $s\concat\<n\>$ for all $n<\omega$ and define $c_{s\concat\<n\>}$, $d_{s\concat\<n\>}$, $c_{s\concat\<n,-1\>}$ for all $n<\omega$ such that
          \[
            d_s < \dots \leq c_{s\concat\<2,-1\>} = c_{s\concat\<1\>} < d_{s\concat\<1\>} \leq c_{s\concat\<1,-1\>} = c_{s\concat\<0\>} < d_{s\concat\<0\>} \leq c_{s\concat\<0,-1\>} = c_{s\concat\<-1\>}
          \]
        where $[c_{s\concat\<n\>}, d_{s\concat\<n\>})\in \mc{C}$ for all $n<\omega$ and $c_{s\concat\<n\>} \rightarrow d_s$.
      \end{itemize}
    \item Suppose $\alpha$ is a limit ordinal and $S_\beta$ has been defined for all $\beta<\alpha$. If $s\in\omega^\alpha$ and $t\in \bigcup_{\beta<\alpha}S_\beta$ for all $t<s$, let $S_\alpha$ contain $s$ and define $d_s = \lim_{t<s}d_t$ and $c_{s\concat\<-1\>} = \lim_{t<s} c_{t\concat\<-1\>}$.
      \item Let $S=\bigcup_{n<\omega} S_\alpha$.
  \end{itemize}

@@

  Finally, we notice that by defining $f\in\omega^\omega_1$ such that $f(\alpha)=n_\alpha$, then $d_{f\rest\alpha}$ is an increasing uncountable sequence defined for all $\alpha<\omega_1$, which is a contradiction.
\end{proof}

### 2013-07-04 phd/menger.tex
Refactored file system

\input{./header.tex}

@@

    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish if there exists a function $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
      \begin{itemize}
        \item $f(\mc{V},n)$ is $\mc{V}$-compact
        \item $f(\mc{V},n)\subseteq f(\mc{V},n+1)$
        \item $\bigcup_{n<\omega}f(\mc{V},n)=X$
        \item The set
          \[
            g(\mc{U},\mc{V},n) = \bigcup_{m\geq n} f(\mc{U},m)\setminus ( f(\mc{U},m-1)\cup f(\mc{V},m))
          \]
         is $\mc{V}$-compact
      \end{itemize}
  \end{definition}

@@

  \begin{proof}
    Let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $f(\mc{U}_{n+1},n+1)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$. If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that $x\in f(\mc{U}_0,N)$ for some $N$. So either $x\in \bigcap_{m\leq N} f(\mc{U}_m,N)$ and is covered by the strategy during round $N$, or for some $m< N$, $x \in f(\mc{U}_m,N)\setminus (f(\mc{U}_{m},N-1)\cup f(\mc{U}_{m+1},N))$ and is covered by the strategy during round $m+1$.
  \end{proof}

>>>>

\input{../header.tex}

@@

    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish if there exists a function $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
      \begin{itemize}
        \item $f(\mc{V},n)$ is $\mc{V}$-compact
        \item $f(\mc{V},n)\subseteq f(\mc{V},n+1)$
        \item $\bigcup_{n<\omega}f(\mc{V},n)=X$
        \item The set
          \[
            g(\mc{U},\mc{V},m+1) = \left(\bigcup_{n\geq m} f(\mc{U},n+1)\setminus f(\mc{V},n+1))\right)\setminus f(\mc{U},0)
          \]
         is $\mc{V}$-compact
      \end{itemize}
  \end{definition}

@@

  \begin{proof}
    Let $\sigma(\mc{U}_0,0)$ cover $f(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $f(\mc{U}_{n+1},n+1)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$. If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that either $x\in f(\mc{U}_0,0)$ and is covered in the initial round, or $x\in f(\mc{U}_0,N+1)$ for some minimal $N$. So one of the following must occur:
      \begin{itemize}
        \item $x\in \bigcup_{m\leq N} f(\mc{U}_{m},0)$ and is covered by the strategy during some round $m\leq N$.
        \item $x\in \bigcap_{m\leq N} f(\mc{U}_{m+1},N+1)$ and is covered by the strategy during round $N+1$.
        \item For some $m \leq N$, 
          \[x \in \Big( f(\mc{U}_{m},N+1)\setminus f(\mc{U}_{m+1},N+1) \Big)\setminus f(\mc{U}_m,0) \subseteq g(\mc{U}_m,\mc{U}_{m+1},m+1)\]
         and is covered during round $m+1$.
      \end{itemize}
  \end{proof}
